### 2008-12-20 talk/ecoop2009/intro.tex
several small fixes.  Some rewording in the cli backend section
add reference to dyla paper, add institute for armin

\cfbolz{we should cite the dyla paper somewhere here. also, we generally need
more references}

PyPy's approach is to automatize the generation of JIT compilers in order
to reduce to a minimum the effort required to get a fast implementation of a
dynamic language; all you have to do is to write a high level specification of
the language (by writing an interpreter), and putting it through PyPy's
translation toolchain. The automatic generation of JIT compilers is done with
the help of partial evaluation techniques.

@@

\anto{as Armin points out, the two CLI backends can be easily confused; what
  about renaming the ``CLI Backend for flowgraphs'' into ``CLI bytecode
  compiler''? Any better idea for the name?}

>>>>

PyPy's approach \cite{RiBo07_223} is to automatize the generation of JIT compilers in order
to reduce to a minimum the effort required to get a fast implementation of a
dynamic language; all you have to do is to write a high level specification of
the language (by writing an interpreter), and putting it through PyPy's
translation toolchain. The automatic generation of JIT compilers is done with
the help of partial evaluation techniques.

@@
